Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Define C_P and aspect ratio

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides a
summary of recent efforts and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance of a
2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D simulations
of a high solidity cross-flow turbine using a $k$--$\epsilon$ renormalization
group (RNG) turbulence model. The results from the 2-D simulations
overpredicted power coefficient since the rotor had a low aspect ratio, while
the 3-D case matched well with wind tunnel measurements near the tip speed ratio
of maximum power. In general, 3-D simulations are less common, but have begun to
appear more frequently recently---a testament to the progress towards higher
computing power.

>>>>

There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al.~\cite{Balduzzi2016} provides a
summary of recent efforts and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly predict performance of a
2-D CFT. Howell et al.~\cite{Howell2010}, performed both 2-D and 3-D simulations
of a high solidity cross-flow turbine using a $k$--$\epsilon$ renormalization
group (RNG) turbulence model. The results from the 2-D simulations overpredicted
power coefficient
\begin{equation}
    C_P = \frac{P}{\frac{1}{2} \rho A U_\infty^3},
    \label{eq:cp}
\end{equation}
where $P$ is the mechanical shaft power, $\rho$ is the fluid density, $A$ is the
rotor frontal area, and $U_\infty$ is the free stream velocity. This was likely
because the rotor had a low aspect ratio (or ratio of height to rotor diameter
$H/D$), while the 3-D case matched well with wind tunnel measurements near the
tip speed ratio of maximum power. In general, 3-D simulations are less common,
but have begun to appear more frequently recently---a testament to the progress
towards higher computing power.
